Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-08-19 manuscript.qmd
trim trailing whitespace
rerun and publish

This consensus was formed as follows: Suppose the involvement status $X_v$ of LNL $v$ was assessed using different diagnostic modalities $\mathcal{O} = \{ \text{MRI}, \text{CT}, \text{pathology}, \ldots \}$, each characterized by their own pair of sensitivity and specificity values $s_N^\mathcal{o}$ and $s_P^\mathcal{o}$, with $\mathcal{o} \in \mathcal{O}$. Then we have $|\mathcal{O}|$ observations $z_v^\mathcal{o} \in \left[ 0, 1 \right]$, where 0 stands for "healthy" and 1 for "involved". We can then compute the most likely true involvement $X_v$ using the likelihood function

$$
\begin{aligned}
\ell \left( X_v \mid \{ z_v^\mathcal{o} \}_{\mathcal{o} \in \mathcal{O}} \right) = \prod_{\mathcal{o} \in \mathcal{O}}
\left( 1 - X_v \right) \cdot &\left[ z_v^\mathcal{o} \cdot \left( 1 - s_P^\mathcal{o} \right) + \left( 1 - z_v^\mathcal{o} \right) \cdot s_P^\mathcal{o} \right] \\
+ X_v \cdot &\left[ z_v^\mathcal{o} \cdot s_N^\mathcal{o} + \left( 1 - z_v^\mathcal{o} \right) \cdot (1 - s_N^\mathcal{o}) \right]
\end{aligned}
$$

>>>>

This consensus was formed as follows: Suppose the involvement status $X_v$ of LNL $v$ was assessed using different diagnostic modalities $\mathcal{O} = \{ \text{MRI}, \text{CT}, \text{pathology}, \ldots \}$, each characterized by their own pair of sensitivity and specificity values $s_N^{\mathcal{o}}$ and $s_P^{\mathcal{o}}$, with $\mathcal{o} \in \mathcal{O}$. Then we have $|\mathcal{O}|$ observations $z_v^{\mathcal{o}} \in \left[ 0, 1 \right]$, where 0 stands for "healthy" and 1 for "involved". We can then compute the most likely true involvement $X_v$ using the likelihood function

$$
\begin{aligned}
\ell \left( X_v \mid \{ z_v^{\mathcal{o}} \}_{\mathcal{o} \in \mathcal{O}} \right) = \prod_{\mathcal{o} \in \mathcal{O}}
\left( 1 - X_v \right) \cdot &\left[ z_v^{\mathcal{o}} \cdot \left( 1 - s_P^{\mathcal{o}} \right) + \left( 1 - z_v^{\mathcal{o}} \right) \cdot s_P^{\mathcal{o}} \right] \\
+ X_v \cdot &\left[ z_v^{\mathcal{o}} \cdot s_N^{\mathcal{o}} + \left( 1 - z_v^{\mathcal{o}} \right) \cdot (1 - s_N^{\mathcal{o}}) \right]
\end{aligned}
$$
